Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-03-13 tensor/draft/draft-tensor-op.tex
[draft-tensor-op] added predictions for B->K* ll angular observables

\documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{multirow}
\usepackage{xcolor}

@@

Both observables exihibit strong suppression factors for vectorial and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensorial and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vectorial couplings of the SM
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensorial couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.

@@

\begin{figure*}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH_1_6_vs_cT}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
\\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability.
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9}
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
  }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{3}{*}{${B\to K^*}$ {form factors}}
    & $V/A_1$ &  $q^2 = 0$ GeV$^2$  & \cite{Hambrock:2013zya} \\
    & $A_0$   &  $q^2 = 0$ GeV$^2$  & \cite{Khodjamirian:2010vf} \\
    & $V$, $A_1$, $A_{12}$
              &  $q^2 = 15,\, 19.21$ GeV$^2$     & \cite{Horgan:2013hoa}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables in the various
  exclusive $b\to s \bar\mu\mu$ decays that enter the fits with their
  respective kinematics and experiments that provide the measurements.
  Lattice results of $B\to K$ form factors are used to constrain their parameters,
  and theoretical constraints on $B\to K^*$ form factors are included. For
  more details see the text and \refapp{app:theory:inputs}.
}
\end{center}
\end{table*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & \eos{$\quad$ $[-0.35,\, 0.20]$ ($[-0.55,\, 0.40]$) $\quad$}
  & \eos{$\quad$ $[-0.20,\, 0.15]$ ($[-0.35,\, 0.30]$) $\quad$}
  & \eos{$\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$}
  \\
  $\mbox{Im}\,\wilson{T}$
  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
  & \eos{$[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
  & \eos{$[-0.10,\, 0.20]$ ($[-0.25,\, 0.35]$)}
  & \eos{$[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)}
  \\
  $\mbox{Im}\,\wilson{T5}$
  & \eos{$[-0.25,\, 0.25]$ ($[-0.45,\, 0.45]$)}
  & \eos{$[-0.15,\, 0.15]$ ($[-0.30,\, 0.30]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\
  \hline
  $|\wilson{T}|$, $|\wilson{T5}|$
  & \eos{$< 0.35$ ($< 0.55$)}
  & \eos{$< 0.25$ ($< 0.35$)}
  & \eos{$< 0.30$ ($< 0.45$)}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $B_s \to \bar\mu\mu$), and $iii)$ allowing
     also new physics contributions to $\wilson{9,\,10}$ with uniform prior
     \eos{$\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-3,\, 3]$}.
  }
\end{table*}

@@

Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
by allowing uniform priors for \eos{$\mbox{Re, Im}(\wilson[NP]{i}) \in[-3,\, 3]$},
($i = 9,10$) in order to access the stability of the bounds derived from $F_H^\mu$
against destructive interference. In this case, $F_H^\mu$ by itself still provides
bounds \eos{$|\wilson{T,\,T5}| < 0.5\,(0.8)$} at 68\% (95\%) probability that are
weakened by a factor of two since $F_H^\mu$ does not pose constraints on
$\wilson{9,\,10}$ (in the chosen prior range). Once additional experimental
measurements of \reftab{tab:observables}
are taken into account, the potential destructive effects of new physics
in $\wilson{9,\,10}$ become reduced and one recovers almost the same
constraints on $\wilson{T,\,T5}$ shown in \reftab{tab:cTT5:1-dimCLs}.
In consequence, the $F_H^\mu$ measurement~\cite{Aaij:2014tfa} of LHCb with
3 fb$^{-1}$ improves the previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$
by a \eos{factor of two}.

@@

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{SM-EFT-constrained scalar couplings}

@@

The couplings $\wilson{S,\, S'}$ can be bound quite reliably from (neglecting
terms of order $m_\ell^2/M_{B_s}^2$ and $m_s/m_b$) \cite{Alonso:2014csa}
\begin{equation}
\begin{aligned}
  \overline{\cal B}(B_s\to \bar\ell\ell) & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2
\\[0.2cm]
  - & \frac{4 m_\ell\, m_b}{M_{B_s}^2} \mbox{Re}
  \left[ (\wilson{S} + \wilson{S'})(\wilson{10} - \wilson{10'})^* \right]
\end{aligned}
\end{equation}
and almost similarly (neglecting terms of order $m_\ell^2/q^2$
and $m_s/m_b$)
\begin{equation}
\begin{aligned}
  F_H^\ell & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2
\\[0.2cm]
  & - \frac{4 m_\ell\, m_b}{q^2} \mbox{Re}
  \left[ (\wilson{S} - \wilson{S'})(\wilson{10} + \wilson{10'})^* \right] \,.
\end{aligned}
\end{equation}

@@

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{Tensorial, scalar and vectorial couplings and
  predictions for $B\to K^* \bar\ell\ell$}

We start with the scenario of the combination of tensorial and scalar couplings
$\wilson{S,S',P,P',T,T5}$, i.e. the combination of the preceding
two sections. In this scenario there are only small changes on the bounds, in fact
they tend to be even more stringent, because tensorial and scalar couplings
can contribute to $F_H^{\mu}$ only constructively --- see \refeq{eq:FH-dependence}.
As before ${\cal B}$'s of $B\to K^{(*)}\bar\mu\mu$ help to strengthen the
constraints on $\wilson{T,\, T5}$. Furthermore we find that even in the case
of complex-valued couplings the data is able to constrain all real and imaginary
parts. In this case, the constraints are even a bit tighter and strong correlations
arise as before among real parts of $\wilson{i}$ and $\wilson{i'}$ for $i = S,P$,
and in addition similarly among their imaginary parts.
\todo{Check this with EOS}

In the remainder we discuss the influence of non-standard $\wilson{10,\, 10'}$,
that play an important role in $\overline{\cal B}(B_s \to \bar\mu\mu)$ ...

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|cc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & NP
  \\
  \hline \hline
  \multirow{2}{*}{$J_{6c}$}
  & $[1.1,\, 6]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  & $[15,\, 19]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  \hline
  \multirow{2}{*}{$J_{1c} + J_{2c}$}
  & $[1.1,\, 6]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  & $[15,\, 19]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  \hline
  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
  & $[1.1,\, 6]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  & $[15,\, 19]$
  & $[ ,\, ]$ ($[ ,\, ]$)
  & $[ ,\, ]$ ($[ ,\, ]$)
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:predictions}
     \todo{predictions for $B\to K^*\bar\ell\ell$}
  }
\end{table*}

>>>>

% vim: set sts=4 et :
\documentclass[prd,preprintnumbers,nofootinbib,twocolumn]{revtex4-1}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{listings}
\usepackage{xcolor}

@@

Both observables exhibit strong suppression factors for vectorial and dipole
couplings present in the SM, thereby enhancing their sensitivity to tensorial and
scalar couplings \cite{Bobeth:2007dw, Bobeth:2012vn}. A similar enhancement of
scalar couplings compared to helicity-suppressed vectorial couplings of the SM 
is well-known from $B_s\to \bar\mu\mu$. Unfortunately the limited data set of
$B\to K^*(\to K\pi) \bar\ell\ell$ from LHCb \cite{Aaij:2013qta} still does not
allow to perform current angular analysis without the assumption of vanishing
scalar and tensorial couplings in this decay mode. In the future also certain
angular observables in $B\to K^* \bar\ell\ell$ will provide additional constraints
on such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz}
and the linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$ 
\cite{Matias:2012xw, Bobeth:2012vn} as well as at low recoil the experimental
test of the relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn}.

@@

\begin{figure*}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
\\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+ 
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability. 
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9} 
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
  }
  \label{fig:FHvsCT}
\end{figure*}

@@

\begin{table*}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\begin{tabular}{lccc}
\hline
Channel & Constraints & Kinematics & Source
\\
\hline \hline
$B_s\to \bar\mu\mu$
& $\int\dd\tau \BR(\tau)$ &  --  & \cite{Aaij:2013aka,Chatrchyan:2013bka,CMS:2014xfa}
\\
\hline
\multirow{2}{*}{${B^+\to K^+ \bar\mu\mu}$}
    & \multirow{2}{*}{$\BR_\mu$}
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll} \\
    &
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014pli} \\
    & $A_{\rm FB}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa, CDF} \\
    & $F_{H}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014tfa} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 22.0]$ GeV$^2$  & \cite{Aaij:2014bsa}    
\\   
\hline
    ${B^0\to K^{\ast 0} \bar\mu\mu}$
    & $\BR_\mu$
    & $q^2\in [1,\, 6],\, [14.18,\, 16],\, [> 16]$ GeV$^2$  & \cite{CDF:2012:BKstarll, Aaij:2013iag,Chatrchyan:2013cda} \\
    & $A_{\rm CP}^\mu$
    &  $\,\,\,\,\, q^2 \in [1.1,\, 6.0],\, [15.0,\, 19.0]$ GeV$^2$  & \cite{Aaij:2014bsa}
\\    
\hline \hline
${B\to K}$ form factors
    & $f_{0,+,T}$   &  $q^2 = 17,\, 20,\, 23$ GeV$^2$  & \cite{Bouchard:2013eph} \\
\hline
\multirow{3}{*}{${B\to K^*}$ {form factors}}
    & $V/A_1$ &  $q^2 = 0$ GeV$^2$  & \cite{Hambrock:2013zya} \\
    & $A_0$   &  $q^2 = 0$ GeV$^2$  & \cite{Khodjamirian:2010vf} \\
    & $V$, $A_1$, $A_{12}$
              &  $q^2 = 15,\, 19.21$ GeV$^2$     & \cite{Horgan:2013hoa}  \\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1.0}
\caption{\label{tab:observables} List of all observables in the various
  exclusive $b\to s \bar\mu\mu$ decays that enter the fits with their
  respective kinematics and experiments that provide the measurements. 
  Lattice results of $B\to K$ form factors are used to constrain their parameters,
  and theoretical constraints on $B\to K^*$ form factors are included. For
  more details see the text and \refapp{app:theory:inputs}.  
}
\end{center}
\end{table*}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.3}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{c|ccc}
  \hline
  data set
  & only $F_H^\mu$
  & $F_H^\mu$ + other
  & $F_H^\mu$ + other
  \\ 
  set of couplings
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5}$
  & $\wilson{T,\,T5,\, 9,\,10}$
  \\
  \hline \hline
  $\mbox{Re}\,\wilson{T}$
  & $\quad$ $[-0.31,\, 0.16]$ ($[-0.51,\, 0.34]$) $\quad$
  & \eos{$\quad$ $[-0.19,\, 0.13]$ ($[-0.34,\, 0.27]$) $\quad$}
  & \eos{$\quad$ $[-0.20,\, 0.20]$ ($[-0.40,\, 0.35]$) $\quad$}
  \\
  $\mbox{Im}\,\wilson{T}$
  & $[-0.23,\, 0.24]$ ($[-0.43,\, 0.43]$)
  & \eos{$[-0.16,\, 0.17]$ ($[-0.31,\, 0.31]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\[0.1cm]
  $\mbox{Re}\,\wilson{T5}$
  & $[-0.24,\, 0.25]$ ($[-0.43,\, 0.44]$)
  & \eos{$[-0.07,\, 0.25]$ ($[-0.23,\, 0.38]$)}
  & \eos{$[-0.20,\, 0.15]$ ($[-0.35,\, 0.35]$)}
  \\
  $\mbox{Im}\,\wilson{T5}$
  & $[-0.25,\, 0.24]$ ($[-0.44,\, 0.44]$)
  & \eos{$[-0.17,\, 0.16]$ ($[-0.31,\, 0.31]$)}
  & \eos{$[-0.20,\, 0.20]$ ($[-0.35,\, 0.35]$)}
  \\
  \hline 
  $|\wilson{T}|$, $|\wilson{T5}|$
  & $[0.13,\, 0.42]$ ($[0.04,\, 0.56]$)
  & \eos{$< 0.25$ ($< 0.35$)}
  & \eos{$< 0.30$ ($< 0.45$)}
  \\
  \hline 
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ --- [upper] 1D-marginalized 
     at 68\% (95\%) probability and [lower] 2D-marginalized --- when using
     measurements of $i)$ only $F_H^\mu$, $ii)$ $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and $iii)$ allowing
     also new physics contributions to $\wilson{9,\,10}$ with uniform prior
     $\mbox{Re},\mbox{Im}(\wilson[NP]{i}) \in [-7,\, 7]$.
  }
\end{table*}

@@

Eventually, we perform a fit with non-zero complex-valued $\wilson{9,\,10}$
by allowing uniform priors for $\mbox{Re, Im}(\wilson[NP]{i}) \in[-7,\, 7]$,
($i = 9,10$) in order to access the stability of the bounds derived from $F_H^\mu$
against destructive interference. In this case, $F_H^\mu$ by itself still provides 
bounds \eos{$|\wilson{T,\,T5}| < 0.5\,(0.8)$} at 68\% (95\%) probability that are
weakened by a factor of two since $F_H^\mu$ does not pose constraints on
$\wilson{9,\,10}$ (in the chosen prior range). Once additional experimental
measurements of \reftab{tab:observables}
are taken into account, the potential destructive effects of new physics
in $\wilson{9,\,10}$ become reduced and one recovers almost the same
constraints on $\wilson{T,\,T5}$ shown in \reftab{tab:cTT5:1-dimCLs}.
In consequence, the $F_H^\mu$ measurement~\cite{Aaij:2014tfa} of LHCb with
3 fb$^{-1}$ improves the previous bounds \cite{Bobeth:2012vn} on $\wilson{T,\,T5}$ 
by a \eos{factor of two}.

@@

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{SM-EFT-constrained scalar couplings \label{sec:SM-EFT}}

@@

The couplings $\wilson{S,\, S'}$ can be bound quite reliably from (omitting
for the sake of the argument terms of order $m_\ell^2/M_{B_s}^2$ and $m_s/m_b$) 
\cite{Alonso:2014csa}
\begin{equation}
\begin{aligned}
  \overline{\cal B}(B_s\to \bar\ell\ell) & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2 
\\[0.2cm]
  - & \frac{4 m_\ell\, m_b}{M_{B_s}^2} \mbox{Re} 
  \left[ (\wilson{S} + \wilson{S'})(\wilson{10} - \wilson{10'})^* \right]
\end{aligned}
\end{equation}
and almost similarly (omitting terms of order $m_\ell^2/q^2$
and $m_s/m_b$)
\begin{equation}
\begin{aligned}
  F_H^\ell & \propto
      \left|\wilson{S} + \wilson{S'}\right|^2
    + \left|\wilson{S} - \wilson{S'}\right|^2 
\\[0.2cm] 
  & - \frac{4 m_\ell\, m_b}{q^2} \mbox{Re} 
  \left[ (\wilson{S} - \wilson{S'})(\wilson{10} + \wilson{10'})^* \right] \,.
\end{aligned}
\end{equation}

@@

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{Tensorial, scalar and vectorial couplings \label{sec:tensor:scalar}}

We start with the scenario of the combination of tensorial and scalar couplings
$\wilson{S,S',P,P',T,T5, 10,10'}$ \todo{(extend this discussion right away to include
also $\wilson{10,\, 10'}$)}, i.e. the combination of the preceding
two sections. In this scenario there are only small changes on the bounds, in fact
they tend to be even more stringent, because tensorial and scalar couplings
can contribute to $F_H^{\mu}$ only constructively --- see \refeq{eq:FH-dependence}.
As before ${\cal B}$'s of $B\to K^{(*)}\bar\mu\mu$ help to strengthen the
constraints on $\wilson{T,\, T5}$. Furthermore we find that even in the case
of complex-valued couplings the data is able to constrain all real and imaginary
parts. In this case, the constraints are even a bit tighter and strong correlations
arise as before among real parts of $\wilson{i}$ and $\wilson{i'}$ for $i = S,P$,
and in addition similarly among their imaginary parts.  
\todo{Check this with EOS}

%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\subsection{ for $B\to K^* \bar\ell\ell$}

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $9,10,T,T5$
  & $10^{(')},S^{(')},P^{(')}$    
  & $10^{(')},S^{(')},P^{(')},T,T5$
  \\
  \hline \hline
  \multirow{2}{*}{$J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & \eos{$(-1.27_{-0.64}^{+3.08}) \cdot 10^{-21}$}
  & \eos{$( 0.01_{-0.12}^{+0.06}) \cdot 10^{-21}$}
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & \eos{$(-0.43_{-0.25}^{+1.06}) \cdot 10^{-21}$}
  & \eos{$(-0.03_{-0.00}^{+0.02}) \cdot 10^{-21}$}
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1c} + J_{2c}$}
  & $[1.1,\, 6]$
  & \eos{$(1.80_{-0.26}^{+0.30}) \cdot 10^{-21}$}
  & \eos{$(3.05_{-0.96}^{+1.31}) \cdot 10^{-21}$}
  & \eos{$(1.22_{-0.17}^{+0.26}) \cdot 10^{-21}$}
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & \eos{$(8.75_{-1.82}^{+2.05}) \cdot 10^{-23}$} 
  & \eos{$(5.63_{-2.58}^{+3.29}) \cdot 10^{-21}$}
  & \eos{$(7.49_{-2.02}^{+1.01}) \cdot 10^{-23}$}
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$J_{1s} - 3 J_{2s}$}
  & $[1.1,\, 6]$
  & \eos{$(2.04_{-0.50}^{+0.57}) \cdot 10^{-22}$}
  & \eos{$(1.46_{-0.60}^{+0.76}) \cdot 10^{-20}$}
  & \eos{SM}
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & \eos{$(5.99_{-1.08}^{+1.19}) \cdot 10^{-23}$} 
  & \eos{$(6.57_{-2.72}^{+3.40}) \cdot 10^{-21}$}
  & \eos{SM}
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline 
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in 
     $B\to K^*\bar\mu\mu$ integrated over
     $q^2$ bins at low- and high-$q^2$ for several new physics scenarios respecting
     all the considered experimental constraints. The SM prediction with respective
     uncertainties are given too, where ``$\simeq 0$'' indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

Eventually, we present the yet allowed ranges due to non-standard tensorial
and scalar couplings of the so far unmeasured angular observables $J_{6c}$,
$(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$ in $B\to K^*(\to K\pi)\bar\ell\ell$
in order to explore the potential of their future measurements in fits of the kind
pursued in this work.
The 68\% probability intervals are collected in \reftab{tab:postdictions} 
for the various general scenarios, i.e. allowing for interference with non-zero
vectorial couplings, in \refsec{sec:tensor}, \refsec{sec:scalar}, 
\refsec{sec:SM-EFT} and \refsec{sec:tensor:scalar} for $q^2$-integrated quantities 
in the low- and high-$q^2$ bins $q^2\in [1.1,\, 6]$ GeV$^2$ and $q^2\in [15,\, 19]$ 
GeV$^2$, respectively. Their posterior distributions have been obtained from the
final posterior samples as explained in~\cite{Beaujean:2012uj}.

For comparison, the SM estimates are also given in \reftab{tab:postdictions}.
At low-$q^2$ they are of order ${\cal O}(10^{-21})$ for $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-23})$ at high-$q^2$ 
due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical 
magnitude of vectorial couplings, note that for example the decay width of 
$B\to K^*\bar\ell\ell$
\begin{align}
  \frac{{\rm d}\Gamma}{{\rm d}q^2} & =
    \frac{2}{3} (3 J_{1s} - J_{2s}) + \frac{1}{3} (3 J_{1c} -  J_{2c}) 
\end{align}
is numerically of the order ${\cal O}(10^{-19})$ in the SM
\begin{equation}
\begin{aligned}
  \langle {\rm d}\Gamma/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
  \eos{\left(1.07_{-0.25}^{+0.28} \right) \cdot 10^{-19}} \,,
\\
  \langle {\rm d}\Gamma/{\rm d}q^2 \rangle_{[\eos{16},\, 19]} & =
  \eos{\left(0.63_{-0.17}^{+0.20} \right) \cdot 10^{-19}} \,,
\end{aligned}
\end{equation}
when integrated over low- and high-$q^2$ regions. On the other hand, $J_{6c}$
is strictly zero for the approximation adopted here. Non-zero contributions
can be generated by QED corrections or potentially from higher-dimensional
($d > 6$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
suppression must be compared to potential suppression present for tensorial
and scalar contributions in particular NP models in order to decide their
relevance. Our model-independent fits are still in a realm where such
considerations insignificant since current experimental measurements, in
combination with theory uncertainties, do not impose yet too stringent
constraints on tensorial and scalar couplings.

Beyond the SM, $J_{6c}$ can get of order ${\cal O}(10^{-21})$ in all considered
scenarios. Concerning $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, substantial
deviations from the SM prediction are possible only in the presence of non-zero
tensorial couplings up to the ${\cal O}(10^{-20})$ at high-$q^2$ and also
at low-$q^2$ in the case of $(J_{1s} - 3\, J_{2s})$.
